\documentclass[10pt,a4paper]{article}

% Set the page margins.
\usepackage[a4paper,margin=0.4in]{geometry}
\usepackage{ragged2e}
\usepackage{enumitem}
\usepackage{parskip}
\usepackage{amssymb}
\usepackage{mathpazo}
\usepackage{textcomp}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

% Setup the language and links
\usepackage[english]{babel}
\usepackage[hidelinks]{hyperref}

% Makes resume-specific commands available.
\usepackage{resume}
\usepackage{fontawesome}

\begin{document}  % start the content of the document
\sloppy  % This is to relax whitespace in favor of straight margins

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}

% ---------------------------------------------------------------------------
% Header
\maintitle{Ozgur Ural, Ph.D.}{}{Last update on \today}

\nobreakvspace{0.1em}

\href{mailto:ozgururalnl@gmail.com}{ozgururalnl@gmail.com} \hfill \textsmaller{\textbar} \hfill
\faLinkedinSquare\ \href{https://www.linkedin.com/in/uralozgur/}{uralozgur} \hfill \textsmaller{\textbar} \hfill
\faGithub\ \href{https://ozgurural.github.io/}{https://ozgurural.github.io} \hfill \textsmaller{\textbar}
\hfill \textsmaller{+}31\ 6\ 2903\ 0434 \hfill \textsmaller{\textbar}
\hfill Leiden, Netherlands

\spacedhrule{0.2em}{0.2em}

% ---------------------------------------------------------------------------
% Professional headline & summary
\roottitle{Senior Software Engineer and Published Researcher \textbar\ PhD in Secure \& Distributed Machine Learning}

Senior software engineer with 11\,+ years of experience delivering enterprise-scale systems and leading cross-functional teams in C++, Java, Scala, and modern web technologies. Completed a PhD (August 2025) in Secure \& Distributed Machine Learning, focusing on proof-of-learning protocols, model watermarking, and large-scale distributed machine learning systems. Architected real-time simulators, led engineering teams of 14+, and consistently translated cutting-edge research into robust production solutions across cybersecurity, aerospace, and enterprise cloud environments.

\spacedhrule{0.9em}{0.1em}
\roottitle{TECHNICAL SKILLS}
\begin{itemize}[leftmargin=*]
  \item \textbf{Languages:} C, C++, Java, Scala, Python, TypeScript/JavaScript
  \item \textbf{Distributed \& Data:} gRPC/Protobuf, Redis, PostgreSQL, REST
  \item \textbf{Systems:} Linux, multithreading, networking, real-time/low-latency, backpressure
  \item \textbf{Web \& UI:} Svelte, HTML, CSS/Tailwind
  \item \textbf{DevOps:} Docker, GitLab CI/CD, Jenkins, Git
\end{itemize}

% ---------------------------------------------------------------------------
\roottitle{EXPERIENCE}

% CURRENT ROLE FIRST
\headedsection
{\href{https://www.aviongroup.aero/}{Avion Full Flight Simulators}}
{\textsc{Nieuw-Vennep, Netherlands}} {

\headedsubsection{Senior Software Engineer}{October 2023 -- Present}
{
        \bodytext{
            \begin{itemize}
                \item Drove technical direction for cloud platform architecture, collaborating with stakeholders to define roadmaps and mentor junior engineers.
                \item Developed real-time simulator software using C, C++, and Scala.
                \item Built a low-latency real-time simulation data pipeline to receive telemetry, normalize/aggregate and serialize to JSON/Protobuf, cache in Redis (hot path), persist in PostgreSQL (durable store), and serve the frontend via gRPC/HTTP; sustained \textasciitilde50\,GB/s real-time ingest with batching and bounded-queue backpressure to keep dashboards responsive.
                \item Built web applications for the Avion Cloud Environment to monitor, configure, and diagnose core simulator components using TypeScript/JavaScript (Svelte), Scala (backend services), Python, gRPC \& Protocol Buffers, HTML, and CSS/Tailwind.
                \item Containerized and deployed services with Docker; implemented caching and storage with Redis and PostgreSQL; automated testing and deployments via GitLab CI/CD.
                \item Translated requirements and specifications into efficient solutions, rapidly prototyping complex systems.
                \item Incorporated multithreading and efficient I/O (sync/async where appropriate) with bounded-queue backpressure to meet rigorous real-time requirements.
            \end{itemize}
        }
}
}

\vspace{0.3cm}

\headedsection
{\href{https://daytonabeach.erau.edu/}{Embry-Riddle Aeronautical University, Daytona Beach}}
{\textsc{Florida, USA}} {
    \headedsubsection
    {Graduate Research Assistant in Electrical Engineering and Computer Science}
    {August 2021 -- August 2025}
    {
        \bodytext
        {
            \begin{itemize}
                \item Thesis Advisor: \href{https://ieeexplore.ieee.org/author/37269327300}{Dr.\ Kenji Yoshigoe}
                \item Dissertation: ``Enhancing Proof-of-Learning Security Against Spoofing Attacks Using Model Watermarking''
            \end{itemize}
        }
    }
}

\vspace{0.3cm}

\headedsection
{\href{https://havelsan.com.tr/en}{Havelsan}}
{\textsc{Ankara, Turkey}}{
    \headedsubsection
    {Software Team Lead}
    {November 2020 -- August 2021}
    {
        \bodytext
        {
            \href{https://havelsan.com.tr/en/sectors/cyber-security/cyber-security/products/havelsan-dlp}{Havelsan DLP} Data Leakage Prevention product.
            \begin{itemize}
                \item Technologies and tools used: C, C++, Java, Go, JavaScript, Qt, Sonar, Pardus, Windows, Git, Jira.
                \item Led a team of 14 engineers (developers, QA, DevOps, support).
                \item Developed and maintained key features of the endpoint agent, ensuring robust data protection.
                \item Coordinated with stakeholders to align project goals with business objectives, ensuring timely delivery.
                \item Provided mentorship and training to team members, fostering a collaborative work environment.
            \end{itemize}
        }
    }
}

\vspace{0.3cm}

\headedsection
{\href{https://www.stm.com.tr/en}{STM Defence Technologies}}
{\textsc{Ankara, Turkey}}{
    \headedsubsection
    {Expert Software Engineer}
    {February 2019 -- November 2020}
    {
        \bodytext
        {
            \href{https://www.stm.com.tr/en/kargu-autonomous-tactical-multi-rotor-attack-uav}{Kargu} Autonomous Rotary-Wing Attack UAV and \href{https://www.stm.com.tr/en/togan}{Togan} Autonomous Multi-Rotor Reconnaissance UAV.
            \begin{itemize}
                \item Technologies and tools used: C++11, Boost, Qt, QML, Google Test, Clang-Tidy, Ubuntu, Git.
                \item Contributed to the architecture and implementation of the mission-control unit, enhancing drone operational capabilities.
                \item Developed components of the ground-control unit using Qt and QML, ensuring effective communication and control.
                \item Designed and implemented Power-On and Continuous Built-In Tests to ensure system reliability and performance.
                \item Worked closely with cross-functional teams to align technical solutions with project requirements and military standards.
            \end{itemize}
        }
    }
}

\vspace{0.3cm}

\headedsection
{\href{https://www.comodo.com}{Comodo Cybersecurity}}
{\textsc{Ankara, Turkey}}{
    \headedsubsection
    {Expert Software Engineer}
    {July 2014 -- February 2019}
    {
        \bodytext
        {
            \href{https://cdome.comodo.com/}{Comodo Dome Secure Web Gateway}, \href{https://www.itarian.com/patch-management.php}{Comodo Patch Manager}, and the Chromium-based web browser \href{https://www.comodo.com/home/browsers-toolbars/browser.php}{Comodo Dragon}.
            \begin{itemize}
                \item Technologies and tools used: C++17, Boost, Qt, Git, Jira, Jenkins, WinAPI, Bitbucket, JavaScript, jQuery.
                \item Led the design and development of Windows services and applications to enhance functionality and reliability.
                \item Established unit testing and code-review protocols to ensure software quality.
                \item Pioneered the development of advanced browser features, enhancing user security and experience.
                \item Developed statistical reporting modules, providing product managers with insights for data-driven decision-making.
                \item Coordinated with cross-functional teams, including product management and QA.
                \item Implemented and maintained CI/CD pipelines using Jenkins.
            \end{itemize}
        }
    }
}

% ---------------------------------------------------------------------------
\spacedhrule{0.9em}{0.1em}

\roottitle{EDUCATION}

\headedsection
{\href{https://daytonabeach.erau.edu/}{Embry-Riddle Aeronautical University, Daytona Beach}}
{\textsc{Florida, USA}} {
    \headedsubsection
    {Ph.D.\ in Electrical Engineering and Computer Science}
    {2021 -- 2025 (conferred August 2025)}
    {
        \begin{itemize}
            \item Dissertation: ``Enhancing Proof-of-Learning Security Against Spoofing Attacks Using Model Watermarking''
        \end{itemize}
    }
}

\vspace{0.3cm}

\headedsection
{\href{http://www.metu.edu.tr/}{Middle East Technical University (METU)}}
{\textsc{Ankara, Turkey}} {
    \headedsubsection
    {Master of Science in Cyber Security}
    {2015 -- 2019}
    {
        \begin{itemize}
            \item Thesis: \href{https://github.com/ozzgural/MSThesis}{Automatic Detection of Cyber Security Events from Turkish Twitter Stream and Turkish Newspaper Data}
        \end{itemize}
    }
}

\vspace{0.3cm}

\headedsection
{\href{http://www.metu.edu.tr/}{Middle East Technical University (METU)}}
{\textsc{Ankara, Turkey}} {
    \headedsubsection
    {Bachelor of Science in Computer Engineering}
    {2010 -- 2014}
    {
        \begin{itemize}
            \item Institutional note: METU is widely regarded as Turkey's leading engineering university and is ranked 269th globally (QS World University Rankings 2026).
        \end{itemize}
    }
}

\vspace{0.3cm}

\headedsection
{\href{https://www.anadolu.edu.tr/en}{Anadolu University}}
{\textsc{Eskişehir, Turkey (Distance/Online)}}{
  \headedsubsection{Bachelor of Business Administration}{2012 -- 2017}{}
}

% ---------------------------------------------------------------------------
\spacedhrule{0.9em}{0.1em}

\roottitle{PUBLICATIONS}
\begin{itemize}
  \item
    {
      Ural, O. (2025). \href{https://commons.erau.edu/edt/905/}{Enhancing Proof-of-Learning Security Against Spoofing Attacks Using Model Watermarking}. Doctoral dissertation, Embry-Riddle Aeronautical University, Daytona Beach, Florida.
    }
  \item
    {
      Ural, O. and Yoshigoe, K. (2025). \href{https://ieeexplore.ieee.org/document/11293969}{SecurePoL: Integration of Watermarking with Proof-of-Learning to Enhance Security Against Spoofing Attacks}. IEEE Access. DOI: 10.1109/ACCESS.2025.3642198.
    }
  \item
    {
      Ural, O. and Yoshigoe, K. (2024). \href{https://ieeexplore.ieee.org/abstract/document/10741282}{Enhancing Security of Proof-of-Learning against Spoofing Attacks using Feature-Based Model Watermarking}. IEEE Access. DOI: 10.1109/ACCESS.2024.3489776.
    }
  \item
    {
      Ural, O. and Yoshigoe, K. (2023). \href{https://doi.org/10.1109/ACCESS.2023.3344669}{Survey on Blockchain-Enhanced Machine Learning}. IEEE Access, pp.\ 145331--145362. DOI: 10.1109/ACCESS.2023.3344669.
    }
  \item
    {
      Ural, O. and Acartürk, C. (2021). \href{https://www.scitepress.org/Papers/2021/102016/102016.pdf}{Automatic Detection of Cyber Security Events from Turkish Twitter Stream and Newspaper Data}. Proceedings of the 7th International Conference on Information Systems Security and Privacy (ICISSP), ISBN 978-989-758-491-6; ISSN 2184-4356, pp.\ 66--76. DOI: 10.5220/0010201600660076.
    }
  \item
    {
      Ural, Ozgur and Erdur, Efe. (2016). \href{https://www.researchgate.net/publication/316102682_Secure_Proxy_on_Cloud}{Secure Proxy on Cloud}. DOI: 10.13140/RG.2.2.24058.08649.
    }
  \item
    {
      Ural, Ozgur (2014). \href{http://senior.ceng.metu.edu.tr/2014/clover}{Autonomous Cargo and Mail Delivery}. Turkish Autonomous Robots Conference, Ankara, Turkey.
    }
  \item
    {
      \textbf{Peer reviewer (2022--present):} Reviewed 10+ manuscripts across machine learning and security venues, including IEEE Access.
    }
\end{itemize}

% ---------------------------------------------------------------------------
\spacedhrule{0.9em}{0.1em}

\roottitle{AWARDS \& HONORS}
\begin{itemize}
    \item The Scientific and Technological Research Council of Turkey (TÜBİTAK) National Project Competition -- First Prize, June 2014.
    \item Middle East Technical University Graduation Projects Competition -- Second Prize, June 2014.
\end{itemize}

\end{document}
