\documentclass[10pt,a4paper]{article}

\usepackage[a4paper,margin=0.4in]{geometry}
\usepackage{ragged2e}
\usepackage{enumitem}
\usepackage{parskip}
\usepackage{amssymb}
\usepackage{mathpazo}
\usepackage{textcomp}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[hidelinks]{hyperref}

% --- resume.sty inlined (commands adapted from Cies Breijs' MIT-licensed
%     resume template, https://github.com/cies/resume) ---
\usepackage{xcolor}
\definecolor{light}{gray}{0.55}
\newcommand{\spacedhrule}[2]{\vspace{#1}\hrule\vspace{#2}}
\newcommand{\maintitle}[3]{\noindent{\LARGE\textbf{#1}}\ifx&#2&\else\quad{\large #2}\fi\hfill{\small\color{light}#3}\par\vspace{0.3em}}
\newcommand{\roottitle}[1]{\par{\large\textbf{#1}}\par\vspace{0.2em}}
\long\def\headedsection#1#2#3{\par\noindent\textbf{#1}\hfill{#2}\par#3\par}
\long\def\headedsubsection#1#2#3{\par\noindent{#1}\hfill{\small{#2}}\par#3}
\long\def\bodytext#1{#1}
% --- end resume.sty ---

\begin{document}
\sloppy
\renewcommand\labelitemi{\textbullet}

\maintitle{Ozgur Ural, Ph.D.}{}{Last update on \today}

\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}} l l l l r}
\href{mailto:drozgurural@gmail.com}{drozgurural@gmail.com} &
+31 6 2903 0434 &
\href{https://linkedin.com/in/uralozgur}{linkedin.com/in/uralozgur} &
\href{https://ozgurural.github.io/}{ozgurural.github.io} &
Amsterdam, Netherlands
\end{tabular*}

\spacedhrule{0.2em}{0.2em}

\roottitle{Machine Learning Research Scientist \& Senior Software Engineer, Ph.D.}

Machine learning research scientist and senior software engineer with 12+ years building production systems across cybersecurity, defense, and simulation, now leading enterprise AI strategy and applied GenAI at Avion. Completed a Ph.D. in Electrical Engineering and Computer Science at Embry-Riddle Aeronautical University in the United States (August 2025), with a machine-learning dissertation and three first-author IEEE Access publications on Proof-of-Learning and model watermarking. My work centers on \textbf{verifiable, trustworthy machine learning}: systems whose behavior can be proven rather than assumed, engineered for domains where failure is not an option.

Deep foundation in systems programming (C, C++, Scala) and distributed architecture, combined with hands-on ML-security research. Experienced in leading engineering teams, owning complex technical deliverables end to end, and translating original research into production-grade systems.

\spacedhrule{0.9em}{0.1em}

\roottitle{TECHNICAL SKILLS}
\begin{itemize}[leftmargin=*]
  \item \textbf{Languages:} C, C++, Scala, Python, Go, Java, TypeScript, JavaScript
  \item \textbf{Systems and real-time:} multithreading, async I/O, low-latency, backpressure, Linux, networking, Boost, Qt/QML
  \item \textbf{Distributed and data:} gRPC, Protobuf, Redis, PostgreSQL, REST, real-time data pipelines
  \item \textbf{Machine learning \& AI:} PyTorch, TensorFlow, scikit-learn, deep learning, LLMs, retrieval-augmented generation (RAG), AI agents, on-prem and air-gapped model deployment, federated and distributed ML training, large-scale model evaluation; trustworthy and verifiable ML (model watermarking, Proof-of-Learning, adversarial robustness, model provenance)
  \item \textbf{Web and UI:} Svelte, TypeScript, HTML, CSS, Tailwind
  \item \textbf{DevOps:} Docker, GitLab CI/CD, Jenkins, Git
\end{itemize}

\roottitle{EXPERIENCE}

\headedsection{\href{https://www.aviongroup.aero/}{Avion Full Flight Simulators}}{\textsc{Amsterdam, Netherlands}}{%
  \headedsubsection{Senior Software Engineer}{Oct 2023 -- Present}{%
    \bodytext{\begin{itemize}
      \item Lead Avion's enterprise AI strategy: authored the AI adoption roadmap and a three-tier architecture spanning air-gapped on-prem LLMs, a governed cloud-LLM API tier, and edge deployment.
      \item Designed a suite of retrieval-augmented and autonomous AI agents (engineering-knowledge copilot with grounded citations and change-impact analysis, autonomous repository agent, RFP accelerator, training-debrief writer) and built the strategy portal end to end (Flask, SQLite, Docker, GitLab CI/CD).
      \item Developed real-time simulator software in C, C++, and Scala.
      \item Built a low-latency data pipeline ingesting simulator telemetry, normalizing and serializing to JSON and Protobuf, caching in Redis, persisting in PostgreSQL, and serving the frontend via gRPC and HTTP; sustained approximately 50 GB/s real-time throughput using batching and bounded-queue backpressure.
      \item Built web applications for the Avion Cloud Environment to monitor, configure, and diagnose core simulator components using TypeScript, Svelte, Scala, Python, and gRPC.
      \item Containerized and deployed services with Docker; automated testing and deployments via GitLab CI/CD.
      \item Applied multithreading and async I/O patterns with backpressure to meet rigorous real-time requirements.
    \end{itemize}}%
  }%
}

\vspace{0.3cm}

\headedsection{\href{https://daytonabeach.erau.edu/}{Embry-Riddle Aeronautical University, Daytona Beach}}{\textsc{Florida, USA}}{%
  \headedsubsection{Graduate Research Assistant}{Aug 2021 -- Aug 2025}{%
    \bodytext{\begin{itemize}
      \item Advisor: \href{https://ieeexplore.ieee.org/author/37269327300}{Dr. Kenji Yoshigoe}. Dissertation: Enhancing Proof-of-Learning Security Against Spoofing Attacks Using Model Watermarking.
      \item Conducted original research on verifiable, trustworthy machine learning across proof-of-learning, model watermarking, and adversarial robustness, with three first-author papers in IEEE Access.
      \item Journal referee for IEEE Access; program committee member for NLPAICS 2026 (University of Alicante).
    \end{itemize}}%
  }%
}

\vspace{0.3cm}

\headedsection{\href{https://havelsan.com.tr/en}{Havelsan}}{\textsc{Ankara, Turkey}}{%
  \headedsubsection{Software Team Lead}{Nov 2020 -- Aug 2021}{%
    \bodytext{\href{https://havelsan.com.tr/en/sectors/cyber-security/cyber-security/products/havelsan-dlp}{Havelsan DLP} enterprise Data Leakage Prevention product.
    \begin{itemize}
      \item Led a team of 14 engineers (developers, QA, DevOps, support) delivering endpoint security software.
      \item Developed and maintained core features of the endpoint agent in C, C++, Java, and Go.
      \item Coordinated with product and business stakeholders to align delivery with roadmap objectives.
    \end{itemize}}%
  }%
}

\vspace{0.3cm}

\headedsection{\href{https://www.stm.com.tr/en}{STM Defence Technologies}}{\textsc{Ankara, Turkey}}{%
  \headedsubsection{Expert Software Engineer}{Feb 2019 -- Nov 2020}{%
    \bodytext{\href{https://www.stm.com.tr/en/kargu-autonomous-tactical-multi-rotor-attack-uav}{Kargu}, Turkey's first indigenous loitering-munition (kamikaze) UAV and an internationally recognized autonomous system, and \href{https://www.stm.com.tr/en/togan}{Togan} Autonomous Reconnaissance UAV.
    \begin{itemize}
      \item Developed critical components of the mission-control and ground-control systems in C++11 with Boost and Qt, under hard-real-time, safety-critical constraints.
      \item Designed and implemented Power-On and Continuous Built-In Tests for system reliability validation.
      \item Worked with cross-functional teams to meet military-grade engineering and safety standards.
    \end{itemize}}%
  }%
}

\vspace{0.3cm}

\headedsection{\href{https://www.comodo.com}{Comodo Cybersecurity}}{\textsc{Ankara, Turkey}}{%
  \headedsubsection{Expert Software Engineer}{Jul 2014 -- Feb 2019}{%
    \bodytext{\href{https://cdome.comodo.com/}{Comodo Dome Secure Web Gateway}, \href{https://www.itarian.com/patch-management.php}{Comodo Patch Manager}, and the \href{https://www.comodo.com/home/browsers-toolbars/browser.php}{Comodo Dragon} browser.
    \begin{itemize}
      \item Led design and development of Windows services and applications in C++17 with Boost and WinAPI.
      \item Established unit testing and code-review practices; implemented CI/CD pipelines with Jenkins.
      \item Developed statistical reporting modules and advanced browser security features.
    \end{itemize}}%
  }%
}

\spacedhrule{0.9em}{0.1em}

\roottitle{EDUCATION}

\headedsection{\href{https://daytonabeach.erau.edu/}{Embry-Riddle Aeronautical University, Daytona Beach}}{\textsc{Florida, USA}}{%
  \headedsubsection{Ph.D. in Electrical Engineering and Computer Science}{Aug 2021 -- Aug 2025}{%
    \begin{itemize}
      \item Dissertation: Enhancing Proof-of-Learning Security Against Spoofing Attacks Using Model Watermarking. Advisor: Dr. Kenji Yoshigoe; committee included IEEE Fellow Dr. Houbing Song.
    \end{itemize}%
  }%
}

\vspace{0.3cm}

\headedsection{\href{http://www.metu.edu.tr/}{Middle East Technical University (METU)}}{\textsc{Ankara, Turkey}}{%
  \headedsubsection{Master of Science in Cyber Security}{2015 -- 2019}{%
    \begin{itemize}
      \item Thesis: \href{https://github.com/ozzgural/MSThesis}{Automatic Detection of Cyber Security Events from Turkish Twitter Stream and Newspaper Data}. Advisor: \href{https://acarturk.net/}{Prof. Cengiz Acart\"urk}.
    \end{itemize}%
  }%
}

\vspace{0.3cm}

\headedsection{\href{http://www.metu.edu.tr/}{Middle East Technical University (METU)}}{\textsc{Ankara, Turkey}}{%
  \headedsubsection{Bachelor of Science in Computer Engineering}{2010 -- 2014}{%
    \begin{itemize}
      \item Turkey's top-ranked and most selective computer engineering program (English-medium): admission among roughly the top 1,000 of more than 2 million national university-entrance candidates.
    \end{itemize}%
  }%
}

\vspace{0.3cm}

\headedsection{\href{https://www.anadolu.edu.tr/en}{Anadolu University}}{\textsc{Eskisehir, Turkey}}{%
  \headedsubsection{Bachelor of Business Administration}{2012 -- 2017}{}%
}

\spacedhrule{0.9em}{0.1em}

\roottitle{PUBLICATIONS}

\begin{itemize}
  \item Ural, O. and Yoshigoe, K. (2025). \href{https://ieeexplore.ieee.org/document/11293969}{SecurePoL: Integration of Watermarking With Proof-of-Learning to Enhance Security Against Spoofing Attacks}. \textit{IEEE Access}, vol. 13, pp. 213067--213091.

  \item Ural, O. and Yoshigoe, K. (2024). \href{https://ieeexplore.ieee.org/abstract/document/10741282}{Enhancing Security of Proof-of-Learning against Spoofing Attacks using Feature-Based Model Watermarking}. \textit{IEEE Access}.

  \item Ural, O. and Yoshigoe, K. (2023). \href{https://doi.org/10.1109/ACCESS.2023.3344669}{Survey on Blockchain-Enhanced Machine Learning}. \textit{IEEE Access}, pp. 145331--145362.

  \item Ural, O. and Acart\"urk, C. (2021). \href{https://www.scitepress.org/Papers/2021/102016/102016.pdf}{Automatic Detection of Cyber Security Events from Turkish Twitter Stream and Newspaper Data}. ICISSP 2021.

  \item Ural, O. (2025). \href{https://commons.erau.edu/edt/905/}{Enhancing Proof-of-Learning Security Against Spoofing Attacks Using Model Watermarking}. Doctoral dissertation, Embry-Riddle Aeronautical University.
\end{itemize}

For full list and citation metrics: \href{https://scholar.google.com/citations?user=lYx8fqsAAAAJ&hl=en&sortby=pubdate}{Google Scholar profile}.

\spacedhrule{0.9em}{0.1em}

\roottitle{PROFESSIONAL SERVICE}

\begin{itemize}
  \item \textbf{Journal Referee:} IEEE Access and peer-reviewed journals in security, machine learning, distributed systems, and blockchain.
  \item \textbf{Program Committee Member (2026):} 2nd Workshop on NLP Applied to Information and Cyber Security (NLPAICS 2026), University of Alicante, Spain.
  \item \textbf{Reviewer:} IEEE and ACM conferences in security, machine learning, and distributed systems.
\end{itemize}

\spacedhrule{0.9em}{0.1em}

\roottitle{AWARDS AND HONORS}

\begin{itemize}
  \item TUBITAK National Project Competition, First Prize, June 2014.
  \item Middle East Technical University Graduation Projects Competition, Second Prize, June 2014.
\end{itemize}

\end{document}
